Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2024-02-02 Text/Articles/MIGARS_2024/Final_Version_MIGARS.Rmd
New version

<!-- In this context, we present a two-stage estimation procedure designed to navigate the complexities of SAR data.  -->
<!-- The first stage tests the hypothesis that the data follow the Gamma distribution, i.e., we are in the presence of fully developed speckle.  -->
<!-- If this hypothesis is rejected, we proceed to the second stage to estimate the parameters that characterize the $\mathcal{G}^0$ distribution.  -->

@@

From \eqref{E:gi01}, the $r$th moment of $Z$ is expressed as:
\begin{align}
	\mathbbm E_{\mathcal{G}_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\gamma(L)}, \quad \alpha <-r. 
	\label{E:rmom}
\end{align}

@@

In Fig.&nbsp;\ref{fig:PlotGammaSAR} we see how the Entropy of the Gamma SAR distribution changes with $\mu$ for various values of $L$.

```{r PlotGammaSAR, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="The Shannon Entropy under the Gamma SAR model."}
L <- c(1, 3, 8, 12, 100)

L_labels <- c(expression(italic(L)==1), 
              expression(italic(L)==3), 
              expression(italic(L)==8), 
              expression(italic(L)==12), 
              expression(italic(L)==100))

entropies <- sapply(L, function(L) entropy_gamma_sar(L, mu))

muEntropy <- data.frame(mu, entropies)

muEntropy.molten <- melt(muEntropy, id.vars = "mu", variable.name = "Looks", value.name = "Entropy")

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = Looks)) +
  geom_line(linewidth=2) +
  theme_minimal() +
  scale_color_manual(values = rainbow(length(L)), labels = L_labels) +
  labs(col = "Looks") +
  xlab(expression(paste(mu))) +
  theme(text=element_text(family="serif"),
        legend.position = "bottom")

<!-- Fig.&nbsp;\ref{fig:3d_GIO} illustrates the entropy of $G_I^0$ distribution as a function of three key parameters: $\mu$, $\alpha$, and $L$. -->

<!-- ```{r 3d_GIO, fig.align="center",  out.width = "70%", fig.cap="The Shannon Entropy under ${G}_I^0$ models.", fig.show="hold",  fig.pos="hbt"} -->
<!-- knitr::include_graphics("../../../Figures/PDF/entropy_plot_3d.pdf") -->
<!-- ``` -->
<!-- As we explore the 3D plot, we can observe how changes in $\mu$, $\alpha$, and $L$ collectively influence the entropy of the $G_I^0$ distribution.  -->
<!-- We can identify regions where entropy is high or low, providing insights into the predictability and structure of the distribution in various regions of the parameter space. -->

@@

The empirical distributions of $\Gamma_{\text{SAR}}$ and $G_I^0$ entropies are shown in Fig.&nbsp;\ref{fig:Plot_empirical_gamma_and_gi0}. 
It is observed that when $\alpha$ approaches negative infinity, the two distributions are very similar. 
In other words, the mean entropy of $G_I^0$ approximates the mean entropy of $\Gamma_{\text{SAR}}$.

```{r Simulated_empirical_gamma_and_gi0, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

R <- 3000
mu <- 1
L <- 8
B <- 1
sample.size <- c(121)
alpha1_values <- c(-3, -8, -20, -1000)

TestStatisticsList <- list()

for (alpha_val in alpha1_values) {
  alpha1 <- alpha_val
  TestStatistics1 <- NULL
  TestStatistics2 <- NULL

    for (r in 1:R) {
      z <- gi0_sample(mu, alpha1, L, s)
      TestStat1[r] <- log(mean(z))  + (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
      TestStat2[r] <- log(mean(z))  + (L - log(L) + lgamma(L) +(1 - L) * digamma(L) - L - lgamma(L - alpha1) + (L - alpha1) * (digamma(L - alpha1)) - (1 - alpha1) * digamma(-alpha1) + log(-1 - alpha1) + lgamma(-alpha1))
    }

    TestStatistics1 <- rbind(TestStatistics1, data.frame("Sample_Size" = rep(s, R), "Test_Statistics" = TestStat1))
    TestStatistics2 <- rbind(TestStatistics2, data.frame("Sample_Size2" = rep(s, R), "Test_Statistics2" = TestStat2))
  }

  TestStatisticsList[[as.character(alpha_val)]] <- list(TestStatistics1 = TestStatistics1, TestStatistics2 = TestStatistics2)
}

save(TestStatisticsList, file = "./Data/data_empirical_entropy.RData")

```{r Plot_empirical_gamma_and_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions of $\\Gamma_{\\text{SAR}}$ and $G_I^0$ entropies as $\\mu=1$, $L=8$ and $\\alpha\\in\\{-1000, -20, -8, -3\\}$."}

load("./Data/data_empirical_entropy.Rdata")
plots_list <- list()

for (alpha_val in alpha1_values) {
  plot_data <- TestStatisticsList[[as.character(alpha_val)]]

  max_density1 <- max(density(plot_data$TestStatistics1$Test_Statistics)$y, na.rm = TRUE)
  max_density2 <- max(density(plot_data$TestStatistics2$Test_Statistics2)$y, na.rm = TRUE)

  plot <- ggplot(plot_data$TestStatistics1, aes(x = Test_Statistics)) +
    geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
    geom_line(data = plot_data$TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
    annotate("text", x = max(plot_data$TestStatistics1$Test_Statistics) + 0.1, y = max_density1,
             label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 5, hjust = 5, color = "red") +
    annotate("text", x = max(plot_data$TestStatistics2$Test_Statistics2) + 0.1, y = max_density2,
             label = TeX("$G_I^0$"), vjust = 5, hjust = 5, color = "blue") +
    labs(x = "Entropy", y = "Density") +
    annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("alpha == %s", alpha_val)), hjust = 1.2, vjust = 1.02, size = 3) +
    theme_minimal() +
    theme(
      text = element_text(family = "serif"),
      legend.position = "none"  
    )

grid.arrange(grobs = plots_list, ncol = 2)

@@

Let's assume that non-parametric entropy estimators \(\widehat{H}=\widehat{\theta}(\bm{Z})\) are inherently biased, that is:
\begin{equation}
\label{Eq:bias1}
\bias\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta.
\end{equation}
Our objective is to devise unbiased estimators with reduced variance. To achieve this, we introduce an "ideal estimator" \(\check{\theta}(\bm{Z})\) using the bias information:
\begin{equation}
\label{Eq:bias2}
\widecheck{\theta}(\bm{Z}) = \widehat{\theta}(\bm{Z}) - \bias\big(\widehat{\theta}(\bm{Z})\big).
\end{equation}
However, \(\check{\theta}(\bm{Z})\) is not an estimator, because it depends on the true parameter \(\theta\), prompting the formulation of a new estimator \(\widetilde{H}\). 
From \eqref{Eq:bias1} and \eqref{Eq:bias2} we have:
\begin{align*}
\widetilde{H} &= 2\widehat{\theta}(\bm{Z}) - \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(\bm{Z}^{(b)}),
\end{align*}
where $B$ is the number of replications in the bootstrap technique.
Applying this methodology, the original estimators by Correa, Ebrahimi, and Al-Omari are now denoted as the proposed bootstrap-enhanced versions: $\widetilde{H}_{\text{C}}$, $\widetilde{H}_{\text{E}}$, and $\widetilde{H}_{\text{AO}}$, respectively.

@@

# Number of replications
R <- 100

# Number of bootstrap replications
B <- 10
mu_values <- c(1, 10)
alpha <- -20
L <- 8

@@

$$
 \begin{cases}\mathcal{H}_0: \widetilde{H}(\bm{Z})-H(\bm{Z})=0 \\ 
  \mathcal{H}_1:\widetilde{H}(\bm{Z})-H(\bm{Z})\neq0 .\end{cases}
$$
In other words, we verify the hypothesis that the data are fully-developed speckle.

For this purpose, we use the following test statistic:
\begin{equation}
\label{Eq:test_e}
S(\bm{Z};L_0)= \widetilde{H}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L_0)+\ln \widebar{\bm{Z}}\right].
\end{equation}
This test statistic $S(\bm{Z};L_0)$ aims to assess the behavior of the data under the null hypothesis, through the empirical distribution of the test statistic values for a sample size of $n$. 
The density should center around zero if the test statistic is capable of detecting that the data are fully-developed speckle, i.e., $S(\bm{Z};L_0)\approx 0$. 
Otherwise, under the alternative hypothesis, the empirical distribution of the test statistic values is not centered around zero. 
This suggests significant differences and implies the presence of heterogeneous clutter.

@@

## The Proposed Test
We analyze the finite sample size behavior of the test statistics defined in \eqref{Eq:test_e}.

Fig. \ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table \ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), coefficient of variation (CV), skewness, kurtosis, and Anderson–Darling $p$-values for normality. 
Results with $p$-values $> 0.05$  indicate no evidence against normality. 
Notably, small variance and near-zero skewness and kurtosis suggest limited spread, symmetry, and light tails. The coefficient of variation shows that as the sample size increases, variability with respect to the mean decreases, aligning with normal distribution expectations.

In Fig. \ref{fig:Plot_normality_qq}, normal QQ-plots visually affirm distributional similarity with the expected normal line, reinforcing our findings.

```{r Simulated_density, echo=FALSE, message=FALSE}
#, cache = TRUE, autodep = TRUE
set.seed(1234567890, kind = "Mersenne-Twister")

R <- 500
mu <- 1
B <- 2
alpha1 <- -8
sample.size <- c(50, 100, 150)
L_values <- c(2, 5, 8, 18)

@@

    mean_val <- mean(TestStat1)
    sd_val <- sd(TestStat1)
    var_val <- var(TestStat1)
    skewness_val <- skewness(TestStat1)
    kurtosis_val <- kurtosis(TestStat1)
   # lillie_p_value <- lillie.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
    ad_p_value <- ad.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
    cv_val <- (sd_val / mean_val)

@@

```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Empirical density  under Gamma SAR model.", fig.width=6, fig.height=5}

@@

We proceeded to explore the capabilities of the proposed test in terms of size and power. Under $\mathcal{H}_0$ the test statistic  is asymptotically distributed as $\mathcal{N}(0,\sigma_S^2))$, and therefore, the $p$-value of the observed test statistic is $2(1-\Phi(\varepsilon))$, where $\Phi$ is the standard Gaussian cumulative distribution function and 
$$
\varepsilon=\frac{\tilde{H}(\bm{Z})-H(\bm{Z})}{\sigma_S}.
$$
Nominal levels of $1\%$, $5\%$, and $10\%$ were considered. In reference to the size, $1000$ simulations have been used for various sample sizes with  satisfactory results. In all cases, the nominal level has been achieved. The power, in general, improves with the increase in the number of looks. The results are presented in Table \ref{tab:table_size_power}, providing a more detailed insight into the effectiveness of the test under different conditions.

```{r Simulated_power, echo=FALSE, message=FALSE}

@@

# Function to calculate p-value
calculate_p_value <- function(test_statistic, mu_W, sigma_W) {
  epsilon <- test_statistic  / sigma_W
  p_value <- 2 * (1 - pnorm(abs(epsilon)))

@@

# Function to calculate Type II Error Rate
calculate_type_II_error_rate <- function(p_values, alpha_nominal) {
  type_II_error_rate <- sum(p_values >= alpha_nominal) / length(p_values)
  return(type_II_error_rate)
}

@@

R <- 500
mu <- 1
L_values <- c(2, 5, 8, 18)
B <- 3
sample_sizes <- c(50, 100, 200, 300)
alpha_nominals <- c(0.01, 0.05, 0.1)

@@

```{r Simulated_error_type_I, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

# Function to calculate p-value
calculate_p_value <- function(test_statistic, mu_W, sigma_W, alpha_nominal) {
  epsilon <- test_statistic / sigma_W
  p_value <- 2 * (1 - pnorm(abs(epsilon)))

  return(p_value < alpha_nominal)  # Return TRUE if p_value is less than alpha_nominal
}

R <- 500
mu <- 1
B <- 3
L_values <- c(2, 5, 8, 18)
sample_sizes <- c( 50, 100, 200, 300)
alpha_nominals <- c(0.01, 0.05, 0.1)

```{r Table_size_and_power, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
cat("\\setlength{\\tabcolsep}{4pt}\n")
# Load Type I Error Rates
load("./Data/type_I_results.Rdata")

@@

# Combine the two datasets based on L and sample size
combined_results <- merge(spread_results, summary_stats, by = c("L", "Sample_Size"))
combined_results <- combined_results %>% 
  arrange(L, Sample_Size)
# Reorder the columns
combined_results <- combined_results %>% 
  select(L, Sample_Size, `0.01.x`, `0.05.x`, `0.1.x`, `0.01.y`, `0.05.y`, `0.1.y`)

# Rename columns
colnames(combined_results) <- c("$L$", "$n$", "$1\\%$", "$5\\%$", "$10\\%$", "$1\\%$", "$5\\%$", "$10\\%$")

@@

# Print the combined table
table_combined_result <- kbl(
  combined_results,
  caption = "Size and Power of the proposed test.",
  format = "latex",
  booktabs = TRUE,
  align = "lcccccccc",
  escape = FALSE,
  digits = 3,
  label = "table_size_power"
)%>%
  add_header_above(c(" ", " ", "Size" = 3,  "Power" = 3)) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")

@@

Fig.&nbsp;\ref{fig:Plot_empirical_test} displays the empirical distributions using statistical test \eqref{Eq:test_e}. Under the null hypothesis, we observe that the densities are centered around zero. Conversely, under the alternative hypothesis, such as for $\alpha=-8$, the density is not centered around zero. It reveals the difference between the entropy of Gamma SAR and $G_I^0$, indicating that we are in a scenario of heterogeneous clutter.

```{r Sim_empirical_test, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}

@@

R <- 3000
mu <- 1
L <- 5
B <- 2
sample.size <- c( 81)

alpha1_values <- c( -2)

@@

```{r Plot_empirical_test, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions under null hypothesis (centered around zero) and alternative hypothesis (e.g., $\\alpha=-8$, showing a shift from zero), with $\\mu=1$ and $L=5$."}

@@

for (alpha_val in alpha1_values) {
  plot <- ggplot(TestStatistics1, aes(x = Test_Statistics)) +
    geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
    geom_line(data = TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
    annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), y=7, parse=TRUE, label="alpha==-8", hjust=-.1, vjust=1.0, col="darkgreen") +
    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-1000, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
    theme_minimal() +
    theme(
      text = element_text(family = "serif"),
      legend.position = "none"  
    )+
    labs(x = "Test Statistics", y = "Density")

@@

## Experiments on Real SAR Images

To assess the practical efficacy of the proposed test, we conducted experiments using real SAR images acquired by the Sentinel-1A system operating in the C band, with  HH polarization, and intensity format. The set of four SAR images, depicted in Fig.&nbsp;\ref{fig:Real_SAR_Images}(a)-(d) represent diverse scenes: a forested area in the Amazonas region, agricultural fields in Flevoland, and urban areas in Berlin and Ottawa, each with sizes of $512 \times 512$ pixels.

We evaluate the test accuracy with small data portions. Ensuring resistance to contamination is crucial, especially in small samples with $5\times 5$, $7\times 7$, or $9\times 9$ windows that may contain data from areas with varying textures. Our assessment determines if the test can produce reasonable estimations, even when some data deviates from the assumed model.

Table&nbsp;\ref{tab:table_sar} shows the results for $5 \times 5$ windows, detailing the performance of the proposed test in accurately identifying the origin of the data. The metadata associated with these original SAR images includes a number of looks $L = 5$.

The openly accessible Sentinel-1 data used in this study was downloaded as Level-1 Ground Range Detected (GRD) products from the Copernicus Data Space Ecosystem (\url{https://dataspace.copernicus.eu}). This format, gaining popularity among operational and application users, containing only the co-polarized and cross-polarized backscatter intensities (VV, VH).

```{r window, fig.align="center",  out.width = "80%", fig.cap=" Sketch of sliding window.", fig.show="hold",  fig.pos="hbt"}
knitr::include_graphics("../../../Figures/PDF/sliding2.pdf")
```

```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.cap='Real SAR images', fig.subcap=c('Amazonas', 'Flevoland','Ottawa', 'Berlin' ), out.width='.48\\linewidth',  fig.ncol=2}
knitr::include_graphics("../../../Figures/PNG/Brazil_Intensity_VV.png")
knitr::include_graphics("../../../Figures/PNG/Flevoland_Intensity_VV.png")
knitr::include_graphics("../../../Figures/PNG/Ottawa_Intensity_VV.png")
knitr::include_graphics("../../../Figures/PNG/Berlin_Intensity_VV.png")
```

```{r SAR_simulations, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
#, cache = TRUE, autodep = TRUE
set.seed(1234567890, kind = "Mersenne-Twister")
x_Brazil <- myread.ENVI(file='../../../Data/SAR/Brazil/Intensity_VV.img', headerfile='../../../Data/SAR/Brazil/Intensity_VV.hdr')
x_Berlin<- myread.ENVI(file='../../../Data/SAR/Berlin/Intensity_VV.img', headerfile='../../../Data/SAR/Berlin/Intensity_VV.hdr')
x_Flevoland <- myread.ENVI(file='../../../Data/SAR/Flevoland/Intensity_VV.img', headerfile='../../../Data/SAR/Flevoland/Intensity_VV.hdr')

x_Flevoland2 <- myread.ENVI(file='../../../Data/SAR/Flevoland2/Intensity_VV.img', headerfile='../../../Data/SAR/Flevoland2/Intensity_VV.hdr')
x_Ottawa <- myread.ENVI(file='../../../Data/SAR/Ottawa/Intensity_VV.img', headerfile='../../../Data/SAR/Ottawa/Intensity_VV.hdr')

L <- 5
B <- 10

# Brazil
nRows_Brazil <- 512
nCols_Brazil <- 512

centerRow_Brazil <- floor(nRows_Brazil / 2)
centerCol_Brazil <- floor(nCols_Brazil / 2)

roiSize_Brazil <- 5

# Coordinates of the ROI
roiStartRow_Brazil <- centerRow_Brazil - floor(roiSize_Brazil / 2) + 1
roiEndRow_Brazil <- roiStartRow_Brazil + roiSize_Brazil - 1

roiStartCol_Brazil <- centerCol_Brazil - floor(roiSize_Brazil / 2) + 1
roiEndCol_Brazil <- roiStartCol_Brazil + roiSize_Brazil - 1

# Extract the ROI
roi_Brazil <- x_Brazil[roiStartRow_Brazil:roiEndRow_Brazil, roiStartCol_Brazil:roiEndCol_Brazil]

mean_data_brasil <- mean(roi_Brazil)
Entropy_brasil <- correa_estimator(roi_Brazil)
entropia_estimada_boot_brasil <- bootstrap_correa_estimator(roi_Brazil, B)
True_entropy_brasil <- (log(mean(roi_Brazil)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
Test_difference_brasil <- bootstrap_correa_estimator_log_mean(roi_Brazil, B) - ((L - log(L) + lgamma(L) + (1 - L) * digamma(L)))

# Berlin
nCols_Berlin = 512
nRows_Berlin = 512

centerRow_Berlin <- floor(nRows_Berlin / 2)
centerCol_Berlin <- floor(nCols_Berlin / 2)

roiSize_Berlin <- 5

# Calculate ROI coordinates
roiStartRow_Berlin <- centerRow_Berlin - floor(roiSize_Berlin / 2) + 1
roiEndRow_Berlin <- roiStartRow_Berlin + roiSize_Berlin - 1

roiStartCol_Berlin <- centerCol_Berlin - floor(roiSize_Berlin / 2) + 1
roiEndCol_Berlin <- roiStartCol_Berlin + roiSize_Berlin - 1

# Extract the ROI
roi_Berlin <- x_Berlin[roiStartRow_Berlin:roiEndRow_Berlin, roiStartCol_Berlin:roiEndCol_Berlin]

mean_data_Berlin <- mean(roi_Berlin)
Entropy_Berlin <- correa_estimator(roi_Berlin)
entropia_estimada_boot_Berlin <- bootstrap_correa_estimator(roi_Berlin, B)
True_entropy_Berlin <- (log(mean(roi_Berlin)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
Test_difference_Berlin <- bootstrap_correa_estimator_log_mean(roi_Berlin, B) - ((L - log(L) + lgamma(L) + (1 - L) * digamma(L)))

# Flevoland
nCols_Flevoland = 512
nRows_Flevoland = 512

centerRow_Flevoland <- floor(nRows_Flevoland / 2)
centerCol_Flevoland <- floor(nCols_Flevoland / 2)

roiSize_Flevoland <- 5

# ROI coordinates
roiStartRow_Flevoland <- centerRow_Flevoland - floor(roiSize_Flevoland / 2) + 1
roiEndRow_Flevoland <- roiStartRow_Flevoland + roiSize_Flevoland - 1

roiStartCol_Flevoland <- centerCol_Flevoland - floor(roiSize_Flevoland / 2) + 1
roiEndCol_Flevoland <- roiStartCol_Flevoland + roiSize_Flevoland - 1

# Extract the ROI
roi_Flevoland <- x_Flevoland[roiStartRow_Flevoland:roiEndRow_Flevoland, roiStartCol_Flevoland:roiEndCol_Flevoland]

>>>>

@@

From&nbsp;\eqref{E:gi01}, the $r$th moment of $Z$ is expressed as:
\begin{align}
	\mathbbm E_{\mathcal{G}_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\gamma(L)}, \quad \alpha <-r. 
	\label{E:rmom}
\end{align}

@@

@@

@@

Let's assume that non-parametric entropy estimators \(\widehat{H}=\widehat{\theta}(\bm{Z})\) are inherently biased, that is:
\begin{equation}
\label{Eq:bias1}
\bias\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta.
\end{equation}
Our objective is to devise unbiased estimators with reduced variance. To achieve this, we introduce an "ideal estimator" \(\check{\theta}(\bm{Z})\) using the bias information:
\begin{equation}
\label{Eq:bias2}
\widecheck{\theta}(\bm{Z}) = \widehat{\theta}(\bm{Z}) - \bias\big(\widehat{\theta}(\bm{Z})\big).
\end{equation}
However, \(\check{\theta}(\bm{Z})\) is not an estimator, because it depends on the true parameter \(\theta\), prompting the formulation of a new estimator \(\widetilde{H}\). 
From&nbsp;\eqref{Eq:bias1} and&nbsp;\eqref{Eq:bias2} we have:
\begin{align*}
\widetilde{H} &= 2\widehat{\theta}(\bm{Z}) - \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(\bm{Z}^{(b)}),
\end{align*}
where $B$ is the number of replications in the bootstrap technique.
Applying this methodology, the original estimators by Correa, Ebrahimi, and Al-Omari are now denoted as the proposed bootstrap-enhanced versions: $\widetilde{H}_{\text{C}}$, $\widetilde{H}_{\text{E}}$, and $\widetilde{H}_{\text{AO}}$, respectively.

@@

# Number of replications
R <- 200

# Number of bootstrap replications
B <- 20
mu_values <- c(1, 10)
alpha <- -20
L <- 8

@@

$$
 \begin{cases}\mathcal{H}_0: \widetilde{H}(\bm{Z})-H_{\Gamma_{\text{SAR}}}(\bm{Z})=0 \\ 
  \mathcal{H}_1:\widetilde{H}(\bm{Z})-H_{\Gamma_{\text{SAR}}}(\bm{Z})\neq0 .\end{cases}
$$
In other words, we verify the hypothesis that the data are fully-developed speckle.
For this purpose, we propose the following test statistic:
\begin{equation}
\label{Eq:test_e}
S(\bm{Z};L_0)= \widetilde{H}_{\text{C}}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L_0)+\ln \widebar{\bm{Z}}\right].
\end{equation}
This test statistic $S(\bm{Z};L_0)$ aims to assess the behavior of the data under the null hypothesis, through the empirical distribution. 
The density should center around zero if the test statistic is capable of detecting that the data are fully-developed speckle, i.e., $S(\bm{Z};L_0)\approx 0$. 
Otherwise, under the alternative hypothesis, the empirical distribution of the test statistic values is not centered around zero. 
This suggests significant differences and implies the presence of heterogeneous clutter.

@@

## The Proposed Test
Fig.&nbsp;\ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table&nbsp;\ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), coefficient of variation (CV), skewness, kurtosis, and Anderson–Darling $p$-values for normality. 
Results with $p$-values $> 0.05$  indicate no evidence against normality. 
Small variance and near-zero skewness and kurtosis suggest limited spread, symmetry, and light tails. The coefficient of variation shows that as the sample size increases, variability with respect to the mean decreases.

In Fig.&nbsp;\ref{fig:Plot_normality_qq}, normal QQ-plots visually affirm distributional similarity with the expected normal line.

```{r Simulated_density, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
#, cache = TRUE, autodep = TRUE
set.seed(1234567890, kind = "Mersenne-Twister")

R <- 1000
mu <- 1
B <- 2
alpha1 <- -8
sample.size <- c(50, 100, 200, 300)
L_values <- c(2, 5, 8, 18)

@@

    mean_val <- mean(TestStat1)
    sd_val <- sd(TestStat1)
    var_val <- var(TestStat1)
    skewness_val <- skewness(TestStat1)
    kurtosis_val <- kurtosis(TestStat1)
   # lillie_p_value <- lillie.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
    ad_p_value <- ad.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
    cv_val <- abs(sd_val / mean_val)

@@

```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Empirical density  under null hypothesis.", fig.width=6, fig.height=5}

@@

After verifying the normality of the data, we proceeded to explore the capabilities of the proposed test in terms of size and power.
Under $\mathcal{H}_0$ the test statistic  is asymptotically distributed as $\mathcal{N}(0,\sigma_S^2))$, and therefore, the $p$-value of the observed test statistic is $2\Phi(\varepsilon)-1$, where $\Phi$ is the standard Gaussian cumulative distribution function and 
$$
\varepsilon=\frac{\tilde{H}(\bm{Z})-H_{\Gamma_{\text{SAR}}}(\bm{Z})}{\sigma_S}.
$$
Nominal levels of $1\%$, $5\%$, and $10\%$ were considered. In reference to the size, $1000$ simulations have been used for various sample sizes with  satisfactory results. In all cases, the nominal level has been achieved. The power, in general, improves with the increase in the sample size and the number of looks. The results are presented in Table&nbsp;\ref{tab:table_size_power}.

```{r Simulated_error_type_I, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
set.seed(1234567890, kind = "Mersenne-Twister")

# 
calculate_p_value <- function(test_statistic, mu_W, sigma_W, alpha_nominal) {
  epsilon <- test_statistic / sigma_W
  p_value <- 2*pnorm(abs(epsilon))-1

  return(p_value < alpha_nominal)  
}

R <- 500
mu <- 1
B <- 2
L_values <- c(2, 5, 8)
sample_sizes <- c( 50, 100, 150, 200)
alpha_nominals <- c(0.01, 0.05, 0.1)

```{r Simulated_power, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}

@@

calculate_p_value <- function(test_statistic, mu_W, sigma_W) {
  epsilon <- test_statistic  / sigma_W
  p_value <- 2 * (1 - pnorm(abs(epsilon)))

@@

calculate_type_II_error_rate <- function(p_values, alpha_nominal) {
  type_II_error_rate <- sum(p_values >= alpha_nominal) / length(p_values)
  return(type_II_error_rate)
}

@@

R <- 500
mu <- 1
L_values <- c(2, 5, 8)
B <- 3
sample_sizes <- c(50, 100, 150, 200)
alpha_nominals <- c(0.01, 0.05, 0.1)

@@

```{r Table_size_and_power, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
cat("\\setlength{\\tabcolsep}{4pt}\n")

load("./Data/type_I_results.Rdata")

@@

combined_results <- merge(spread_results, summary_stats, by = c("L", "Sample_Size"))
combined_results <- combined_results %>% 
  arrange(L, Sample_Size)

combined_results <- combined_results %>% 
  select(L, Sample_Size, `0.01.x`, `0.05.x`, `0.1.x`, `0.01.y`, `0.05.y`, `0.1.y`)

colnames(combined_results) <- c("$L$", "$n$", "$1\\%$", "$5\\%$", "$10\\%$", "$1\\%$", "$5\\%$", "$10\\%$")

@@

table_combined_result <- kbl(
  combined_results,
  caption = "Size and Power of the proposed test.",
  format = "latex",
  booktabs = TRUE,
  align = "lcccccccc",
  escape = FALSE,
  digits = 3,
  label = "table_size_power"
)%>%
  add_header_above(c(" ", " ", "Size" = 3,  "Power" = 3)) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")

@@

Fig.&nbsp;\ref{fig:Plot_empirical_test} displays the empirical distributions using the test statistical&nbsp;\eqref{Eq:test_e}. Under the null hypothesis, the density centers around zero.

```{r Sim_empirical_test, echo=FALSE, message=FALSE}

@@

R <- 500
mu <- 1
L <- 5
B <- 5
sample.size <- c( 81)

alpha1_values <- c( -8)

@@

```{r Plot_empirical_test, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions under null hypothesis (centered around zero) and alternative hypothesis (e.g., $\\alpha=-8$, showing a shift from zero), with $\\mu=1$ and $L=5$."}

@@

for (alpha_val in alpha1_values) {
  plot <- ggplot(TestStatistics1, aes(x = Test_Statistics)) +
    geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
    geom_line(data = TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
    annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), y=6, parse=TRUE, label="alpha==-8", hjust=-.1, vjust=1.0, col="darkgreen") +
    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-1000, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
    theme_minimal() +
    theme(
      text = element_text(family = "serif"),
      legend.position = "none"  
    )+
    labs(x = "Test Statistics", y = "Density")

@@

## Application to Actual Data

We applied the test statistical to a real SAR image of Flevoland province, Netherlands, acquired by the Sentinel-1A system operating in the C band, with  HH polarization, and intensity format.
This image has $300 \times 300$ pixels and covers two different areas, urban areas and agricultural fields. 
The metadata associated with these original SAR images includes a number of looks $L = 5$.

Fig.&nbsp;\ref{fig:Real_SAR_Images}(a) shows the SAR image, from which we selected $7 \times 7$ local sliding windows covering the entire image. 
The test statistical is applied to each window. 
In Fig.&nbsp;\ref{fig:Real_SAR_Images}(b), the test results and corresponding $p$-values, computed over each $7\times 7$ sample, are shown as pixels. 
This assessment aims to determine the test's effectiveness in identifying data origin. 
The new image reveals two distinct regions: lighter backgrounds indicate homogeneity, while darker backgrounds represent heterogeneous areas.

```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.cap='Results of applying the test statistical to actual data.', fig.subcap=c('SAR image.', '$p$-values calculated.' ), out.width='.48\\linewidth',  fig.ncol=2}
knitr::include_graphics("../../../Figures/PNG/Intensity.png")
knitr::include_graphics("../../../Figures/PNG/pvalue7x7.png")
